### 2024-01-07 documentation/thesis/thesis_abstract.tex
more thesis
more thesis - first external review

Especially in the construction of low-field MRI devices based on
permanent magnets, a large number of magnets are used. In order to
realize a homogeneous B0 field with these magnets, which is necessary
for many setups, the magnetic properties of these magnets should be as
similar as possible.

Due to the complex manufacturing process, especially of neodymium
magnets, the different properties, especially the direction of
magnetization, can deviate from each other, which affects the
homogeneity of the field.

To adjust the field afterwards, a passive shimming process is typically
performed, which is complex and time-consuming and requires manual
corrections to the magnets used.

To avoid this process, magnets can be systematically measured in
advance. However, in this methodology, the recording, data storage and
subsequent evaluation of the data play an important role.

The various existing solutions implement individual aspects, but do not
provide a data pipeline from aqusation to analysis.

For this use case, the MagneticReadoutProcessing library was created,
which implements different aspects of data acquisition, data storage,
analysis, and each intermediate step can be customized by the user
without having to create everything from scratch, favoring an exchange
between different user groups.

>>>>

A large number of magnets are used in the construction of low-field MRI
equipment on the basis of permanent magnets. The magnetic properties of
these magnets must be similar to a certain degree in order to achieve a
homogeneous B0 field, which is necessary for many setups. Due to the
complex manufacturing process of neodymium magnets, the different
properties, i.e.~the direction of magnetisation, can deviate from each
other. This affects the homogeneity of the field. A passive shimming
process is typically used to adjust the field afterwards. This is
complex and time-consuming and requires manual corrections to the
magnets used. To avoid this process, magnets can be systematically
measured in advance. Data acquisition, storage and subsequent analysis
play an important role in this methodology. Several existing open source
solutions implement individual parts, but do not provide a complete data
processing pipeline from acquisition to analysis, and their data storage
formats are not compatible with each other. For this use case, the
MagneticReadoutProcessing library has been created. It implements all
important aspects of acquisition, storage and analysis, and each
intermediate step can be customised by the user without having to create
everything from scratch, thus encouraging exchange between different
user groups. Complete documentation, tutorials and tests enable users to
use and adapt the framework as quickly as possible. The framework was
used to characterise different magnets, which requires integrating
magnetic field sensors.
